---
title: "CPSC 335 Algorithm Engineering"
output: html_document
runtime: shiny
---

# Project 1
## Group Members: Sean Mitchell, Jason Mora-Mendoza

# 1. Mathematical Analysis

# 2. Implementation in C++

## Random Problem Generation
## Algorithm Implementation

# 3. Empirical Analysis
In this section, we will be empirically analyzing the performance of both the
mean problem and the construct matrix problem.
```{r libraries, include=FALSE}
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
```
## Mean Problem Scatterplot
What is the efficiency class of the `mean` algorithm? mean runs in O(n) time.
We predict that if we implement the `mean` algorithm in C++ then measure its performance on 
a large amount of inputs n, the points will fit a straight line T(N) = c*n for some constant slope c.

```{r mean_problem_scatterplot}
meanExecutionTimes <- read_csv("mean.csv")
ggplot(meanExecutionTimes, aes(x = n, y = `time elapsed (ms)`, color=`time elapsed (ms)`)) + geom_point() + geom_smooth(color="red") + ggtitle("Mean Problem Growth")
```

## Matrix Problem Scatterplot
```{r matrix_problem_scatterplot}
matrixExecutionTimes <- read_csv("matrix.csv")
ggplot(matrixExecutionTimes, aes(x = n, y = `time elapsed (ms)`, color=`time elapsed (ms)`)) + geom_point() + geom_smooth(color="red") + ggtitle("Matrix Problem Growth")
```
